Gráfico de control T2 Hotelling para variables cualitativas

### 2021-11-12 ArticleHotellingACM/ArticleHotellingACM.Rmd
UPD

```{r diagram, echo=FALSE, fig.align='center',results='asis', fig.pos="H", out.extra = "", out.width='40%', fig.width=16, fig.height=9}
knitr::include_graphics("/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/ktables.png")
```

@@

```{r , echo=FALSE, fig.align='center',results='asis', fig.pos="h", out.extra = "", out.width='90%', fig.width=16, fig.height=9}
knitr::include_graphics("/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/ktablesMCA.png")
```

@@

```{r , echo=FALSE, fig.align='center',results='asis', fig.pos="H", out.extra = "", out.width='60%', fig.width=16, fig.height=9}
knitr::include_graphics("/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/DescrPack.png")
```

@@

```{r , echo=FALSE, fig.align='center',results='asis', fig.pos="H", out.extra = "", out.width='80%', fig.width=18, fig.height=12}
knitr::include_graphics("/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/ArticleHotellingACM/conjuntosensibilidad.png")
```

>>>>

```{r diagram, echo=FALSE, fig.align='center',results='asis', fig.pos="H", out.extra = "", out.width='40%', fig.width=16, fig.height=9}
knitr::include_graphics("ktables.png")
```

@@

```{r , echo=FALSE, fig.align='center',results='asis', fig.pos="h", out.extra = "", out.width='90%', fig.width=16, fig.height=9}
knitr::include_graphics("ktablesMCA.png")
```

@@

```{r , echo=FALSE, fig.align='center',results='asis', fig.pos="H", out.extra = "", out.width='60%', fig.width=16, fig.height=9}
knitr::include_graphics("DescrPack.png")
```

@@

```{r , echo=FALSE, fig.align='center',results='asis', fig.pos="H", out.extra = "", out.width='80%', fig.width=18, fig.height=12}
knitr::include_graphics("conjuntosensibilidad.png")
```

### 2021-11-12 ArticleHotellingACM/ArticleHotellingACM.tex
UPD

\begin{center}\includegraphics[width=0.4\linewidth,]{/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/ktables} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth,]{/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/ktablesMCA} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth,]{/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/DescrPack} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth,]{/Users/javierrojas/Documents/ESTAD EXTRAS/HotellingACM/ArticleHotellingACM/conjuntosensibilidad} \end{center}

>>>>

\begin{center}\includegraphics[width=0.4\linewidth,]{ktables} \end{center}

@@

\begin{center}\includegraphics[width=0.9\linewidth,]{ktablesMCA} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth,]{DescrPack} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth,]{conjuntosensibilidad} \end{center}
